Writing a reproducible paper with R Markdown and Pagedown^[Corresponding adress: mail@paulcbauer.eu, camille.landesvatter@mzes.uni-mannheim.de]

### 2021-06-23 paper.Rmd
Updated keywords

---
title: "Writing a reproducible paper with R Markdown and Pagedown^[Corresponding adress: mail@paulcbauer.eu, camille.landesvatter@mzes.uni-mannheim.de]"
shorttitle: "Writing a reproducible paper with R Markdown and Pagedown"
author:
  - name: Paul C. Bauer
    affiliation: Mannheim Centre for European Social Research
    email: <mail@paulcbauer.eu>
  - name: Camille Landesvatter
    affiliation: Mannheim Centre for European Social Research
    email: <camille.landesvatter@mzes.uni-mannheim.de>
date: 'First version: 20 June, 2021<br>This version: `r format(Sys.time(), "%d %B, %Y")`'
download-link: 'Download: https://osf.io/k8jhx'
abstract: 'The present paper provides a template to write a reproducible scientific paper with R Markdown and Pagedown.^[Based on an earlier R Markdown template that uses Latex and can be downloaded under https://osf.io/q395s [see @Bauer2018-dl].] Below we outline some of the "tricks"/code (e.g., referencing tables, sections etc.) we had to figure out to produce this document. The underlying files which produce this document can be [downloaded here](https://drive.google.com/drive/folders/1rWzj-Bu1EKqkSuE1gaFzduBJhzlThpkw?usp=sharing). Importantly, we also provide different CSS and HTML files that can be used to achieve a pdf output with the look of a "working paper". We are convinced that in the future there will be many improvements and developments with regards to RStudio, R markdown and Pagedown. We intend to update this file when we discover more convenient code. You can follow any updates on the [github repository](https://github.com/paulcbauer/Writing_a_reproducable_paper_in_pagedown/.'
# at least one keyword must be supplied
keywords: [open science, transparency, replication, R, markdown, pagedown]
links-to-footnotes: false
paged-footnotes: true
bibliography: references.bib
output: 
  pagedown::jss_paged:
    template: wp_paged.html
    self_contained: true
    css: ['wp.css', 'wp-fonts.css', 'wp-page.css']
    csl: american-sociological-association.csl
# uncomment the next line if you only want to knit to HTML and not PDF
knit: pagedown::chrome_print
---

>>>>

---
title: "Writing a reproducible paper with R Markdown and Pagedown^[Corresponding adress: mail@paulcbauer.eu, camille.landesvatter@mzes.uni-mannheim.de]"
shorttitle: "Writing a reproducible paper with R Markdown and Pagedown"
author:
  - name: Paul C. Bauer
    affiliation: Mannheim Centre for European Social Research
    email: <mail@paulcbauer.eu>
  - name: Camille Landesvatter
    affiliation: Mannheim Centre for European Social Research
    email: <camille.landesvatter@mzes.uni-mannheim.de>
date: 'First version: 20 June, 2021<br>This version: `r format(Sys.time(), "%d %B, %Y")`'
download-link: 'Download: https://osf.io/k8jhx'
abstract: 'The present paper provides a template to write a reproducible scientific paper with R Markdown and Pagedown.^[Based on an earlier R Markdown template that uses Latex and can be downloaded under https://osf.io/q395s [see @Bauer2018-dl].] Below we outline some of the "tricks"/code (e.g., referencing tables, sections etc.) we had to figure out to produce this document. The underlying files which produce this document can be [downloaded here](https://drive.google.com/drive/folders/1rWzj-Bu1EKqkSuE1gaFzduBJhzlThpkw?usp=sharing). Importantly, we also provide different CSS and HTML files that can be used to achieve a pdf output with the look of a "working paper". We are convinced that in the future there will be many improvements and developments with regards to RStudio, R markdown and Pagedown. We intend to update this file when we discover more convenient code. You can follow any updates on the [github repository](https://github.com/paulcbauer/Writing_a_reproducable_paper_in_pagedown/).'
# at least one keyword must be supplied
keywords: [open science, transparency, replication, reproducible research, reproducibility, R, markdown, pagedown]
links-to-footnotes: false
paged-footnotes: true
bibliography: references.bib
output: 
  pagedown::jss_paged:
    template: wp_paged.html
    self_contained: true
    css: ['wp.css', 'wp-fonts.css', 'wp-page.css']
    csl: american-sociological-association.csl
# uncomment the next line if you only want to knit to HTML and not PDF
knit: pagedown::chrome_print
---
